Domestication and the impacts of linked selection on the maize genome

### 2015-08-11 manuscript.tex
updates

\begin{figure*}[!htb]
%\vspace*{.05in}
\centering
\includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_Significance_June}
\hspace{0.05\textwidth} \includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvT_Folded2_Significance_June}
\caption{Pairwise diversity surrounding synonymous and non-synonymous
  substitutions in maize and teosinte. \jri{a bit too much vertical white space} {\bf A:} Maize diversity; {\bf B:} Teosinte
diversity. Bootstrap-based 95\% confidence intervals are depicted via shading. Inset plots depict a larger range on the x-axis. \label{fig:hardSweeps}}
\end{figure*}

%%%%
%%%% This outline no longer needed in-text because results headers follow
%%%%
% \jri{
% {\bf Outline}
% \begin{enumerate}
% \item Diversity differs between genes, not genes
% \item No hard sweeps
% \item soft sweeps? (putting it here means if we find a lot we may have to redo stuff below on the subset of genes w/o evidence of soft sweeps.)
% \item purifying selection differs ($\pi$)
% \item Estimating the bneck
% \item purifying selection (singletons)
% \item fit the B curve
% \item simulations
% \end{enumerate}
% }

>>>>

\begin{figure*}[!htb]
%\vspace*{.05in}
\centering
\includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_Significance_Aug}
\hspace{0.05\textwidth} \includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvT_Folded2_Significance_Aug}
\caption{Pairwise diversity surrounding synonymous and non-synonymous
  substitutions in maize and teosinte. {\bf A:} Maize diversity; {\bf B:} Teosinte
diversity. Bootstrap-based 95\% confidence intervals are depicted via shading. Inset plots depict a larger range on the x-axis. \label{fig:hardSweeps}}
\end{figure*}
